---
title: 'Predicting Heart Disease '
output:
  pdf_document: default
  html_notebook: default
---


```{r}
library(tidyverse)
library(tidymodels)
library(corrr)
```
reading csv files
```{r}
heart<-read.csv("heart.csv")
```
#exploring and finding data set
```{r}
skimr::skim(heart)
```
```{r}
glimpse(heart)
```

```{r}
heart %>% select(where(~!is.character(.x))) %>% corrr::correlate() %>% network_plot()
```


after watching this plot we get to know that there is relation between Age,maxhr,heartdisease,oldpeak and
the fastingBS and cholestrol can be related and restingBP has no relation with any heart disease
, but we have only select numeric value in this case so let start spltting data and training data



#Preprocessing
```{r}
d_split<-initial_split(heart)
d_train<-training(d_split)
d_test<-testing(d_split)

```

```{r}
data_recp<-recipe(HeartDisease~.,d_train) %>% 
  step_mutate(HeartDisease=ifelse(HeartDisease==0,"NO","YES")) %>% 
  step_dummy(all_nominal(),-all_outcomes()) %>% prep()
  
```

```{r}
juiced<-juice(data_recp)
```

```{r}
bake(data_recp,d_train)
```

#algorithm to model
```{r}
log_heart<-logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification") %>% fit(HeartDisease~.,data=bake(data_recp,d_train))
```

```{r}
final_model<-log_heart %>% 
  predict(new_data=bake(data_recp,d_test)) %>% bind_cols(bake(data_recp,d_test) %>% select(HeartDisease))
final_model

```
so the preiction is ready now we will see if model is sucessfully predicting value or not

```{r}
final_model %>% 
  conf_mat(HeartDisease,.pred_class)
```
so with the help of confusion matrix we get to know that right now our model is perfprming well and les see its recall rate and precission
```{r}
final_model %>% metrics(HeartDisease,.pred_class) %>% select(-.estimator,) %>% filter(.metric=="accuracy")
```

```{r}
final_model %>%
  precision(HeartDisease,.pred_class) %>% filter(.metric=="precision") %>% select(-.estimator)
```
```{r}
final_model %>% 
  recall(HeartDisease,.pred_class)%>% filter(.metric=="recall") %>% select(-.estimator)
```







